NLIZE: A Perturbation-Driven Visual Interrogation Tool for Analyzing and Interpreting Natural Language Inference Models: Supplemental Materials

### 2018-03-31 paper/application.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Scenario 5: Handcraft Example Exploration}
To test the limits of the model, domain experts often handcraft ``extreme'' examples (such as the Facebook IPO example discussed in Section~\ref{sec:languageInference}) for which they know most models will have difficulty making a correct inference.
%
The researchers start with a set of experiments they plan to run, from which they will develop new hypotheses for further analysis.
%
In some way, we can think of such a process as a natural blend of all previously discussed scenarios. However, instead of having a specific goal in mind, the domain experts focus on probing around to uncover any interesting or out-of-the-ordinary behaviors in the model.
%

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Scenario 5: Handcrafted Example Exploration}
To test the limits of the model, domain experts often handcraft ``extreme'' examples (such as the Facebook IPO example discussed in Section~\ref{sec:languageInference}) for which they know most models will have difficulty making a correct inference.
%
The researchers start with a set of experiments they plan to run, from which they will develop new hypotheses for further analysis.
%
In some way, we can think of such a process as a natural blend of all previously discussed scenarios. However, instead of having a specific goal in mind, the domain experts focus on probing around to uncover any interesting or out-of-the-ordinary behaviors in the model.
%
